To do list for this paper

### 2017-09-20 PaperToDo.Rmd
update to do -- cool 50 pages....

- [ ] Write an abstract - Gelman method/sanity check. First sentence of every paragraph of the intro & the very last sentence of intro. 
- [ ] Submit to journal
- [X] Spacing around figures WAY to large above/below captions - change fig.height for coord_fixed figures 
- [X] Make axes labels and text larger in figures
- [X] Make labels of points larger

@@

- [ ] Proof read

@@

- [ ] Proof read
- [X] Make sure I've defined ego/alter nodes
- [ ] Need to talk about the CTMC, rest of the SAOM model definition after the objective function discussion.

@@

- [ ] Proof read
- [ ] Finish section 3.1 (elaborate on probability)

@@

- [ ] Add histogram of number of tie changes from $t_1$ to $t_2$ in simulations 
- [ ] Add another example of a data set for M-in-DS (Sect 4.1) (Congress)
- [ ] Make gif available online
- [ ] Insert link to full gif in paper
- [X] Figure 6: reverse order of adjacency matrix y-axis
- [X] Figure 5: get rid of Vs on node labels, make font bigger
- [X] Figure 7 not showing up??
- [X] Fix error on p. 21 (probably related to above)
- [X] Heatmap p 23 missing caption
- [X] Describe Figure 8 more. What is going on??
- [ ] Add geomnet example in 4.2
- [X] p. 26-28 figure refs & code is broken
- [X] Get rid of repeated plot p 29
- [X] p. 34 code is broken
- [ ] General proof reading

>>>>

- [X] Write an abstract - Gelman method/sanity check. First sentence of every paragraph of the intro & the very last sentence of intro. 
- [ ] Submit to journal
- [X] Spacing around figures WAY to large above/below captions - change fig.height for coord_fixed figures 
- [X] Make axes labels and text larger in figures
- [X] Make labels of points larger
- [X] Reverse order of x-y axes on adjmat vizs

@@

- [X] Proof read

@@

- [X] Proof read
- [X] Make sure I've defined ego/alter nodes
- [X] Need to talk about the CTMC, rest of the SAOM model definition after the objective function discussion.

@@

- [X] Proof read
- [X] Finish section 3.1 (elaborate on probability)
- [ ] Beef up transition after sect. 3.1.3

@@

- [X] Add another example of a data set for M-in-DS (Sect 4.1) (Congress)
- [ ] Make node-link gif available online
- [ ] Insert link to full node-link gif in paper
- [ ] Make adjmat gif available online
- [ ] Insert link to full adjmat gif in paper
- [ ] Beef up transition before Sect 4.4
- [X] Figure 6: reverse order of adjacency matrix y-axis
- [X] Figure 5: get rid of Vs on node labels, make font bigger
- [X] Figure 7 not showing up??
- [X] Fix error on p. 21 (probably related to above)
- [X] Heatmap p 23 missing caption
- [X] Describe Figure 8 more. What is going on??
- [X] Add geomnet example in 4.2
- [X] p. 26-28 figure refs & code is broken
- [X] Get rid of repeated plot p 29
- [X] p. 34 code is broken
- [X] General proof reading
